---
title: "Anthony Rebours's CV"
author: Anthony Rebours
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "C:/Users/rebou/OneDrive/Bureau/Stats/R/Projets/cv/spreadsheets/",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _C:/Users/rebou/OneDrive/Bureau/Stats/R/Projets/cv/_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](C:/Users/rebou/OneDrive/Bureau/Stats/R/Projets/cv/rebours_cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV |> print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

**Language** \
- French (Native)\
- English (Fluent)

**Software** \
- Gephi \
- RMarkdown \
- Jupyter(Python)

**R Programming** \
- Network Analysis \
- Bibliometrics \
- Statistics \
- Data visualization \
- web-scraping

**SQL Programming** \
- Database querying and data formating

```{r}
# CV |> print_skill_bars()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available [on github.com/nstrayer/cv](https://github.com/nstrayer/datadrivencv).




Main
================================================================================

Anthony Rebours {#title}
--------------------------------------------------------------------------------

```{r}
# Note the assignment back to CV. This is so the link stripping works properly in PDF mode
CV <- print_text_block(CV, "intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'education')
```



Teachning and Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'teaching_and_research_experiences')
```



Research Articles {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'research_articles')
```

<!-- These breaks just force a new page so section doesnt get cut off -->
<br>
<br>
<br>

Working Papers {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'working_papers')
```



Blog Posts {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'blog_posts')
```



Talks  {data-icon=person-chalkboard}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'talks')
```


<br>
<br>


Elected Positions  {data-icon=handshake}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'elected_positions')
```



Grants {data-icon=landmark}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'grants')
```




